smooth-sea

### 2018-05-30 index.rmd
updating to reflect bym as top model

pred <- sea_f %>%
  mutate(rent = spt_Med) %>%
  filter(listingQtr == as.yearqtr(Sys.Date())) %>%
  mutate(var = paste0(as.yearqtr(Sys.Date()), " Forecast")) %>%
  dplyr::select(GISJOIN, long, lat, group, rent, var, actualRent, spt_Med, NAMELSAD10, n1B)

comb <- bind_rows(obs, pred) %>%
  mutate(tooltip = paste0(NAMELSAD10, "<br>", "Forecast: $", round(spt_Med), "<br>", "Qtr-to-Date: $", round(actualRent), "<br>", "N Qtr-to-Date: ", n1B))
comb <- SharedData$new(comb, ~GISJOIN)

@@

Model abbr.                   | Description
----------------------------- | -----------------------------------------------
**int**    | Quarter fixed intercept
           | `r format(form.int, )`
**ns**     | Non-spatial tract random effect for each tract, quarter fixed intercept
           | `r format(form.ns)`
**nsar1**  | Non-spatial tract random effect, AR(1) random effect for prior quarter, i.i.d random effect for current quarter
           | `r format(form.nsar1)`
**bym**    | Spatial intrinsic conditional autoregressive (ICAR) tract random-effect, non-spatial i.i.d tract random effect, AR(1) random effect for prior quarter, i.i.d random effect for current quarter
           |  `r format(form.bym)`
**spt**    | Spatial intrinsic conditional autoregressive (ICAR) tract random-effect, non-spatial i.i.d tract random effect, AR(1) random effect for prior quarter, i.i.d random effect for current quarter, i.i.d. random effect for tract-quarter (space-time interaction)
           | `r format(form.spt)`

>>>>

pred <- sea_f %>%
  mutate(rent = bym_Med) %>%
  filter(listingQtr == as.yearqtr(Sys.Date())) %>%
  mutate(var = paste0(as.yearqtr(Sys.Date()), " Forecast")) %>%
  dplyr::select(GISJOIN, long, lat, group, rent, var, actualRent, bym_Med, NAMELSAD10, n1B)

comb <- bind_rows(obs, pred) %>%
  mutate(tooltip = paste0(NAMELSAD10, "<br>", "Forecast: $", round(bym_Med), "<br>", "Qtr-to-Date: $", round(actualRent), "<br>", "N Qtr-to-Date: ", n1B))
comb <- SharedData$new(comb, ~GISJOIN)

@@

Model abbr.                   | Description
----------------------------- | -----------------------------------------------
**int**    | Quarter fixed intercept
           | `r format(form.int)`
**ns**     | Non-spatial tract random effect for each tract, quarter fixed intercept
           | `r format(form.ns)`
**nsar1**  | Non-spatial tract random effect, AR(1) random effect for prior quarter, i.i.d random effect for current quarter
           | `r format(form.nsar1)`
**bym**    | Spatial intrinsic conditional autoregressive (ICAR) tract random-effect, non-spatial i.i.d tract random effect, AR(1) random effect for prior quarter, i.i.d random effect for current quarter
           |  `r format(form.bym)`
**spt**    | Spatial intrinsic conditional autoregressive (ICAR) tract random-effect, non-spatial i.i.d tract random effect, AR(1) random effect for prior quarter, i.i.d random effect for current quarter, i.i.d. random effect for tract-quarter (space-time interaction)
           | `r format(form.spt)`
